---
title: "Results"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
library(targets)
library(tidyverse)
library(DT)
library(dagitty)
```

## Analysis Specifications

Specify relevant results:

```{r}
exposures <- c("eczema")
outcomes <- c("fractures")
models <- c("crude", "adjusted_sex", "adjusted_sex_bmi")
exclusions <- c("none", "lymphoma")
```

Specify relevant DAG:
```{r}
dag <- tar_read(DAGs)[["confounder_adjusted_simple"]]
```


## Inputs {.tabset}

### Included

The following combinations of inputs are relevant for this study:

```{r echo=FALSE}
#Filter results based on given specifications
results <- tar_read(results_regression) %>% 
    filter(term %in% exposures,
           exposure %in% exposures,
           outcome %in% outcomes,
           model %in% models,
           exclusion %in% exclusions)

results %>% 
    select(exposure, outcome, model, exclusion) %>% 
    datatable()
```

### Excluded

The following combinations of inputs are not relevant for the selected exposures and outcomes and were dropped:

```{r echo=FALSE}
results_dropped <- tar_read(results_regression) %>% 
    filter(
        (term %in% exposures &
             exposure %in% exposures &
             outcome %in% outcomes)
        &
            (!(model %in% models) |
                 !(exclusion %in% exclusions)
            )
    )

results_dropped %>% 
    select(exposure, outcome, model, exclusion) %>% 
    datatable()

```

### DAG

The following DAG was chosen as the most appropriate for these analyses
```{r}
plot(dag)
```


## Results

```{r}
results %>% 
    ggplot(aes(x=model, y=estimate)) +
    geom_pointrange(aes(ymin=conf.low, ymax=conf.high)) +
    coord_flip() +
    geom_hline(yintercept=1, lty=2)

```
